### 2017-08-29 natural-deduction.tex
introduction + related work

The term assignment for natural deduction of the commutative part of the model, i.e. the SMCC of
the adjunction, is defined in Figure~\ref{fig:elle-nd-smcc}. And the term assignme for the
non-commutative part, i.e. the Lambek category of the adjunction, is defined in
Figure~\ref{fig:elle-nd-lambek}. $[[P]]$ and $[[I]]$ are contexts for the non-commutative part
and they are lists. $[[G]]$ and $[[D]]$ are contexts for the commutative part and they are
multisets, therefore the following exchange rules are implicit.
\scriptsize
\begin{mathpar}
  \ottdruleTXXbeta{} \qquad\qquad \ottdruleSXXbeta{}
\end{mathpar}

\begin{figure}[!h]
 \scriptsize
  \begin{mdframed}
    \begin{mathpar}
      \ottdruleTXXid{} \qquad\qquad \ottdruleTXXunitI{} \qquad\qquad \ottdruleTXXunitE{} \\
      \ottdruleTXXtenI{} \qquad\qquad \ottdruleTXXtenE{} \\
      \ottdruleTXXimpI{} \qquad\qquad \ottdruleTXXimpE{} \qquad\qquad \ottdruleTXXGI{}
    \end{mathpar}
  \end{mdframed}
\caption{Commutative Part}
\label{fig:elle-nd-smcc}
\end{figure}

\begin{figure}[!h]
 \scriptsize
  \begin{mdframed}
    \begin{mathpar}
      \ottdruleSXXid{} \qquad\qquad \ottdruleSXXunitI{} \qquad\qquad \ottdruleSXXunitEOne{} \\
      \ottdruleSXXunitETwo{} \qquad\qquad \ottdruleSXXunitEThree{} \\
      \ottdruleSXXunitEFour{} \qquad\qquad \ottdruleSXXtenI{} \\
      \ottdruleSXXtenEOne{} \qquad\qquad \ottdruleSXXtenETwo{} \\
      \ottdruleSXXimprI{} \qquad\qquad \ottdruleSXXimprE{} \qquad\qquad \ottdruleSXXimplI{} \\
      \ottdruleSXXimplE{} \qquad\qquad \ottdruleSXXFI{} \\
      \ottdruleSXXFE{} \qquad\qquad \ottdruleSXXGE{}
    \end{mathpar}
  \end{mdframed}
\caption{Non-Commutative Part}
\label{fig:elle-nd-lambek}
\end{figure}

@@

>>>>

The term assignment for natural deduction of the commutative part of the model, i.e. the SMCC of
the adjunction, is defined in Figure~\ref{fig:elle-nd-smcc}. And the term assignme for the
non-commutative part, i.e. the Lambek category of the adjunction, is defined in
Figure~\ref{fig:elle-nd-lambek}. $[[P]]$ and $[[I]]$ are contexts for the commutative part
and they are multisets. $[[G]]$ and $[[D]]$ are contexts for the mix of the commutative part and
the non-commutative part, and they are lists. Therefore the following exchange rule is implicit.

\begin{figure}[!h]
  \scriptsize
  \begin{mathpar}
    \NDdruleTXXbeta{}
  \end{mathpar}
\end{figure}

\begin{figure}[!h]
  \scriptsize
  \begin{mdframed}
    \begin{mathpar}
      \NDdruleTXXid{} \qquad\qquad \NDdruleTXXunitI{} \qquad\qquad \NDdruleTXXunitE{} \\
      \NDdruleTXXtenI{} \qquad\qquad \NDdruleTXXtenE{} \\
      \NDdruleTXXimpI{} \qquad\qquad \NDdruleTXXimpE{} \qquad\qquad \NDdruleTXXGI{} \\
      \NDdruleSXXbeta{}
    \end{mathpar}
  \end{mdframed}
\caption{Commutative Part}
\label{fig:elle-nd-smcc}
\end{figure}

\begin{figure}[!h]
 \scriptsize
  \begin{mdframed}
    \begin{mathpar}
      \NDdruleSXXid{} \qquad\qquad \NDdruleSXXunitI{} \qquad\qquad \NDdruleSXXunitEOne{} \\
      \NDdruleSXXunitEOne{} \qquad\qquad \NDdruleSXXunitETwo{} \\
      \NDdruleSXXtenI{} \qquad\qquad \NDdruleSXXtenEOne{} \\
      \NDdruleSXXtenETwo{} \qquad\qquad \NDdruleSXXimprI{} \\
      \NDdruleSXXimprE{} \qquad\qquad \NDdruleSXXimplI{} \\
      \NDdruleSXXimplE{} \qquad\qquad \NDdruleSXXGE{} \qquad\qquad \NDdruleSXXFI{} \\
      \NDdruleSXXFE{}
    \end{mathpar}
  \end{mdframed}
\caption{Non-Commutative Part}
\label{fig:elle-nd-lambek}
\end{figure}

We could derive exchange comonadically as follows:

@@

We also have the three cut rules derivable in the natural deduction:

\begin{figure}[!h]
  \scriptsize
  \begin{mathpar}
    \NDdruleTXXcut{} \qquad\qquad \NDdruleSXXcutOne{} \qquad\qquad \NDdruleSXXcutTwo{}
  \end{mathpar}
\end{figure}

\begin{center}
  \tiny
  \begin{math}
  $$\mprset{flushleft}
  \inferrule* [right={\tiny FI}] {
    {[[I |-c t : X]]}
  }{[[I |-l F t : F X]]}
  \end{math}
\end{center}

### 2017-08-29 sequent-calculus-ott.tex
introduction + related work

The term assignment for sequent calculus of the commutative part of the model, i.e. the SMCC of
the adjunction, is defined in Figure~\ref{fig:elle-smcc}.

\begin{figure}[!h]
 \scriptsize
  \begin{mdframed}
    \begin{mathpar}
      \ottdruleTXXid{} \qquad\qquad \ottdruleTXXunitI{} \qquad\qquad \ottdruleTXXunitE{} \\
      \ottdruleTXXtenI{} \qquad\qquad \ottdruleTXXtenE{} \\
      \ottdruleTXXimpI{} \qquad\qquad \ottdruleTXXimpE{} \qquad\qquad \ottdruleTXXGI{}
    \end{mathpar}
  \end{mdframed}
\caption{Commutative Part}
\label{fig:elle-nd-smcc}
\end{figure}

>>>>

The term assignment for sequent calculus of the commutative part of the model, i.e. the SMCC of
the adjunction, is defined in Figure~\ref{fig:elle-smcc}. And the term assignme for the
non-commutative part, i.e. the Lambek category of the adjunction, is defined in
Figure~\ref{fig:elle-lambek}. $\Psi$ and $\Phi$ are contexts for the non-commutative part
and they are lists. $\Gamma$ and $\Delta$ are contexts for the commutative part and they are
multisets, therefore the following exchange rules are implicit.

\begin{mathpar}
\scriptsize
\end{mathpar}

\begin{figure}[!h]
 \scriptsize
  \begin{mdframed}
    \begin{mathpar}
    \end{mathpar}
  \end{mdframed}
\caption{Commutative Part}
\label{fig:elle-nd-smcc}
\end{figure}
